Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-18 paper/paper.tex
This sentence no longer applies
slight reformatting
Table formatting
Prettier graphs

\begin{table}[p]
\centering
\begin{tabularx}{.8\textwidth}{XXrXrrrXrrrr}
\toprule
Class && \VFtwo && \multicolumn{3}{c}{\LAD} && \multicolumn{4}{c}{\hspace*{2em}\Glasgow}\\
&&&&incomplete&default&path&&1&2&3&4\\
\midrule
1 &&        0 &&       20 &        0 &        0 &&       80 &        0 &        0 &        0 \\
2 &&      201 &&       92 &      189 &      270 &&      520 &      180 &       53 &       15 \\
3 &&      112 &&     1608 &      617 &      959 &&      396 &      195 &       21 &        0 \\
4 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
5 &&      266 &&        0 &        1 &        3 &&       31 &        0 &        0 &        0 \\
6 &&       71 &&        0 &        0 &        0 &&        7 &       14 &        1 &        0 \\
7 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
8 &&        0 &&        0 &        0 &        1 &&      195 &       69 &        6 &        0 \\
9 &&       77 &&        3 &        0 &       19 &&      103 &        1 &        0 &        0 \\
10 &&       13 &&        0 &        2 &        2 &&        7 &        0 &        0 &        0 \\
11 &&        2 &&      142 &       71 &       17 &&       23 &        0 &        0 &        0 \\
12 &&        0 &&        0 &        1 &        2 &&      158 &        6 &        1 &        0 \\
\midrule
Total && 1282 && 1865 & 881 & 1273 && 1530 & 465 & 82& 15\\
\bottomrule \\
\end{tabularx}
\caption{Number of times each algorithm is best, for each class.\label{expClass}}
\end{table}

@@

\caption{Number of solved instances over time for the virtual best
solver, \LLAMA, and individual solvers (shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}) on the reduced set of 2336 instances.}
\label{fig:portfolio-ecdf}
\end{figure}

@@

Figure~\ref{fig:portfolio-ecdf-full} shows the number of solved instances over time for the
algorithm selection system including \IncompleteLAD and \VFtwo presolving on the full set of
instances. Note that for very easy instances, we are better than the virtual best solver because
\IncompleteLAD is not included in our portfolio. The performance on small instances is much better
than the \LLAMA selector alone (cf.\ Figure~\ref{fig:portfolio-ecdf}) and the region where \LLAMA
performs worse than the individual solvers is now limited to approximately $10^2$ to $10^5$
milliseconds.

@@

\begin{figure}[p]
    \input{graph-full}
\caption{Number of solved instances over time for the virtual best
solver, \LLAMA, and individual solvers (shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}) on the full set of 5725 instances.}
\label{fig:portfolio-ecdf-full}
\end{figure}

>>>>

\begin{table}[p]
    \centering\setlength{\tabcolsep}{0.2em}
\begin{tabularx}{.85\textwidth}{XXrXrrrXrrrr}
\toprule
Class && \VFtwo && \multicolumn{3}{c}{\LAD} && \multicolumn{4}{c}{\Glasgow}\\
      &&&&\textsc{Incomplete}&\textsc{Default}&\textsc{Path}&&\multicolumn{1}{c}{\textsc{1}}&\multicolumn{1}{c}{\textsc{2}}&\multicolumn{1}{c}{\textsc{3}}&\multicolumn{1}{c}{\textsc{4}}\\
\midrule
1 &&        0 &&       20 &        0 &        0 &&       80 &        0 &        0 &        0 \\
2 &&      201 &&       92 &      189 &      270 &&      520 &      180 &       53 &       15 \\
3 &&      112 &&     1608 &      617 &      959 &&      396 &      195 &       21 &        0 \\
4 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
5 &&      266 &&        0 &        1 &        3 &&       31 &        0 &        0 &        0 \\
6 &&       71 &&        0 &        0 &        0 &&        7 &       14 &        1 &        0 \\
7 &&      270 &&        0 &        0 &        0 &&        5 &        0 &        0 &        0 \\
8 &&        0 &&        0 &        0 &        1 &&      195 &       69 &        6 &        0 \\
9 &&       77 &&        3 &        0 &       19 &&      103 &        1 &        0 &        0 \\
10 &&       13 &&        0 &        2 &        2 &&        7 &        0 &        0 &        0 \\
11 &&        2 &&      142 &       71 &       17 &&       23 &        0 &        0 &        0 \\
12 &&        0 &&        0 &        1 &        2 &&      158 &        6 &        1 &        0 \\
\midrule
Total && 1282 && 1865 & 881 & 1273 && 1530 & 465 & 82& 15\\
\bottomrule \\
\end{tabularx}
\caption{Number of times each algorithm is best, for each class.\label{expClass}}
\end{table}

@@

\caption{Number of solved instances over time for the virtual best solver,
\LLAMA, and the single best solver \GlasgowTwo on the reduced set of 2336
instances. Other individual solvers are shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}. }
\label{fig:portfolio-ecdf}
\end{figure}

@@

Figure~\ref{fig:portfolio-ecdf-full} shows the number of solved instances over
time for the algorithm selection system including \IncompleteLAD and \VFtwo
presolving on the full set of instances. The performance on small instances is
much better than the \LLAMA selector alone (cf.\
Figure~\ref{fig:portfolio-ecdf}) and the region where \LLAMA performs worse than
the individual solvers is now limited to approximately $10^2$ to $10^5$
milliseconds.

@@

\begin{figure}[p]
    \input{graph-full}
\caption{Number of solved instances over time for the virtual best solver,
\LLAMA, and the single best solver \GlasgowTwo on the full set of 5725
instances. Other individual solvers are shown as dotted lines, in the same
colours as Figure~\ref{expTimeGraph}. }
\label{fig:portfolio-ecdf-full}

\end{figure}
